---
title: "Pilot Study Results"
author: "Ramiro Casó - Rotterdam School of Management"
date: "`r Sys.Date()`"
output:
  html_document:
    css: custom.css
    theme: journal
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.table.format = "html")
```


```{r libraries}
library(kableExtra)
library(knitr)
library(tidyverse) # Includes ggplot2, dplyr, and other data manipulation libraries
library(readr)
library(rstatix)
library(ggpubr)

```


# Intro

Hello Bram, Steven, how are you? 

This is the final report of the current pilot. I think we are going to need to find a new set of stimuli, because results are not promising, even after collecting the second batch (the one without the visual aid)

I'm going to present the analysis in this HTML, which I hope doesn't become to long. We can discuss it further in our next meeting. 

---


```{r loading the data}
exp_data <- read_csv("study2b_total.csv")
exp_data[, c(46, 51, 56)] <- lapply(exp_data[, c(46, 51, 56)], as.factor)
```

# Data Cleaning

First, and just like you suggested, I'm using the two batches together and included a new variable called `pilot` which differentiates the first batch (pilot_a = with visual aid) from the second batch (pilot_b = without visual aid)

Second, I'm removing participants that either answer to fast (below 5 minutes) or took too long (above 20 minutes). 

Here is a histogram of `duration_min` along with the summary statistics. 

As it can be observed, there are a few observations that answer in less than 5 minutes and some that took almost 40 min. 


```{r cleaning}

ggplot(exp_data, aes(x = duration_min)) +
  geom_histogram(binwidth = 2, fill = "blue", alpha = 0.7) +
  labs(title = "Duration in Min",
       x = "Duration (Minutes)",
       y = "Frequency") +
  theme_minimal()

# Calculate the summary statistics
duration_summary <- summary(exp_data$duration_min)

# Create a data frame to hold the summary
summary_df <- data.frame(
  Statistic = c("Minimum", "1st Quartile", "Median", "Mean", "3rd Quartile", "Maximum"),
  Value = c(duration_summary[1], duration_summary[2], duration_summary[3], mean(exp_data$duration_min), duration_summary[5], duration_summary[6])
)

# Round the values to 2 decimal points
summary_df$Value <- round(summary_df$Value, 2)

kable(summary_df, format = "html", caption = "Summary of Duration (Minutes)", align = c("c", "c"), row.names = FALSE)


```


---

My idea is to trim this data so that I only keep those above the 10th percentile and below the 95 percentile. 

Here are the resulting histogram and descriptives of `duration_min`.


```{r triming}


# Calculate the 5th and 95th percentiles of duration_min
#lower_bound <- quantile(exp_data$duration_min, 0.10)
#upper_bound <- quantile(exp_data$duration_min, 0.90)

lower_bound <- 5  # Lower bound set to 5 minutes
upper_bound <- 30 # Upper bound set to 20 minutes


# Filter the data to retain only observations between the 5th and 95th percentiles
#exp_data_t <- exp_data[exp_data$duration_min > lower_bound & exp_data$duration_min < upper_bound, ]

exp_data_t <- exp_data[exp_data$duration_min > lower_bound & exp_data$duration_min < upper_bound & exp_data$pilot == "pilot_b", ]

ggplot(exp_data_t, aes(x = duration_min)) +
  geom_histogram(binwidth = 2, fill = "blue", alpha = 0.7) +
  labs(title = "Duration in Min",
       x = "Duration (Minutes)",
       y = "Frequency") +
  theme_minimal()

# Calculate the summary statistics
duration_summary <- summary(exp_data_t$duration_min)

# Create a data frame to hold the summary
summary_df <- data.frame(
  Statistic = c("Minimum", "1st Quartile", "Median", "Mean", "3rd Quartile", "Maximum"),
  Value = c(duration_summary[1], duration_summary[2], duration_summary[3], mean(exp_data_t$duration_min), duration_summary[5], duration_summary[6])
)

# Round the values to 2 decimal points
summary_df$Value <- round(summary_df$Value, 2)

kable(summary_df, format = "html", caption = "Summary of Duration (Minutes)", align = c("c", "c"), row.names = FALSE)



```


# Descriptives

Here is a table with the mean, standard deviation, and \( n \). For clarity, these are the names of the variables.

- `text_type`: The main independent variable indicating the type of text that was presented, which has three levels: `met_a`= metaphor apt; `met_na= non-apt metaphor; and `literal` = control condition.  
- `ave_sk_t1`: Mean Subjective Knowledge before presenting the Text (Time 1).
- `ave_sk_t2`: Mean Subjective Knowledge after presenting the Text (Time 2).
- `ave_sk_t3`: Mean Subjective Knowledge after presenting the Objective Knowledge Scale (Time 3).
- `ave_wta`: Average of the Willingness to Adopt scale. 
- `total_ok`: Results of Objective Knowledge Scale calculated by adding the correct answers. 
- `duration_min`: Average time it took to complete the survey in minutes. 

```{r descriptives}

# Compute means and standard errors

variables <- c("ave_sk_t1", "ave_sk_t2", "ave_sk_t3","total_ok","ave_wta", "duration_min")

data_summary <- exp_data_t %>%
  gather(variable, value, all_of(variables)) %>% # Using all_of for variable selection
  group_by(variable) %>% # Grouping by variable only
  summarise(
    mean = mean(value, na.rm = TRUE),
    se = sd(value, na.rm = TRUE) / sqrt(n()),
    p10 = quantile(value, 0.10, na.rm = TRUE), # 10th percentile
    p25 = quantile(value, 0.25, na.rm = TRUE), # 25th percentile
    p50 = quantile(value, 0.50, na.rm = TRUE), # 50th percentile (median)
    p75 = quantile(value, 0.75, na.rm = TRUE), # 75th percentile
    n = n()
  )


data_summary_grouped <- exp_data_t %>%
  gather(variable, value, all_of(variables)) %>% # Using all_of for variable selection
  group_by(text_type, variable) %>%
  summarise(
    mean = mean(value, na.rm = TRUE),
    se = sd(value, na.rm = TRUE) / sqrt(n()),
    p10 = quantile(value, 0.10, na.rm = TRUE), # 10th percentile
    p25 = quantile(value, 0.25, na.rm = TRUE), # 25th percentile
    p50 = quantile(value, 0.50, na.rm = TRUE), # 50th percentile (median)
    p75 = quantile(value, 0.75, na.rm = TRUE), # 75th percentile
    n = n()
  )

## First table

data_summary %>%
  kable(format = "html", digits = 2, align = 'c', caption = "Summary Statistics for All Variables") %>%
  kable_styling(full_width = FALSE)

# Creating a table for data_summary_grouped
data_summary_grouped %>%
  kable(format = "html", digits = 2, align = 'c', caption = "Summary Statistics for Groped Variables") %>%
  kable_styling(full_width = FALSE)


```


---

# Subjective Knowledge

Now that I have cleaned the data, let's analyze it, starting with the subjective knowledge scale. 

Again, for clarity, keep in mind that: 

- `ave_sk_t1`: Mean Subjective Knowledge before presenting the Text (Time 1).
- `ave_sk_t2`: Mean Subjective Knowledge after presenting the Text (Time 2).
- `ave_sk_t3`: Mean Subjective Knowledge after presenting the Objective Knowledge Scale (Time 3).

First, let's run an a simple Repeated measured ANOVA

## SK ANOVA's

```{r sk}

sk_df <- exp_data_t %>%
  select(ResponseId, ave_sk_t1, ave_sk_t2, ave_sk_t3, text_type, pilot) %>%
  pivot_longer(
    cols = c(ave_sk_t1, ave_sk_t2, ave_sk_t3),
    names_to = "sk_time",
    values_to = "ave_sk"
  )
```

```{r sk ANOVA}


# Conduct the repeated measures ANOVA
#anova_sk <- aov(ave_sk ~ sk_time + pilot + Error(ResponseId/sk_time), data = sk_df)

anova_sk <- aov(ave_sk ~ sk_time + Error(ResponseId/sk_time), data = sk_df)


# Print the summary
summary(anova_sk)

# Calculate the means and standard errors
sk_summary <- sk_df %>%
  group_by(sk_time) %>%
  summarise(
    n_obs = n(),
    mean_ave_sk = mean(ave_sk, na.rm = TRUE),
    se_ave_sk = sd(ave_sk, na.rm = TRUE) / sqrt(n()),
    .groups = "drop" # This line avoids a warning message
  )

# Formatting the table with kable and kableExtra
sk_summary %>%
  kable("html") %>%
  kable_styling("striped", full_width = FALSE) %>%
  add_header_above(c("Time Point" = 1, "Number of Observations" = 1, "Subjective Knowledge" = 2)) %>%
  column_spec(2:3, bold = TRUE, color = "blue")


# Create the plot
ggplot(sk_summary, aes(x=sk_time, y=mean_ave_sk, group=1)) +
  geom_line(color="blue") + # Line connecting the points
  geom_point(size=3, color="red") + # Points for the means
  geom_errorbar(aes(ymin=mean_ave_sk - se_ave_sk, ymax=mean_ave_sk + se_ave_sk), width=0.2) + # Error bars
  labs(
    title="Effect of SK Time on Average SK",
    x="SK Time",
    y="Average SK"
  ) +
  ylim(1, 7) + # Set the limits of the Y-axis
  theme_minimal()


```


---
Here are the results for a mixed two-way ANOVA

```{r sk mixed anova}

# Load the necessary libraries
library(nlme)
library(car) # For Type III SS

# Ensure that sk_time and text_type are factors
sk_df$sk_time <- factor(sk_df$sk_time)
sk_df$text_type <- factor(sk_df$text_type)
sk_df <- na.omit(sk_df)


# Fit the model with sk_time as a within-subjects factor, text_type as a between-subjects factor, and a random intercept for each subject

model <- lme(ave_sk ~ text_type * sk_time, random = ~1 | ResponseId, data = sk_df)

#model <- lme(ave_sk ~ text_type * sk_time + pilot, random = ~1 | ResponseId, data = sk_df)



# Use the Anova function from the car package to get Type III SS
mix_anova_sk <- Anova(model, type = "III")

# Print the result
print(mix_anova_sk)

```


```{r sk mixed anova visualization}
# Calculate the means and standard errors for each combination of text_type and sk_time

sk_summary <- sk_df %>%
  group_by(text_type, sk_time) %>%
  summarise(
    n_obs = n(),
    mean_ave_sk = mean(ave_sk, na.rm = TRUE),
    se_ave_sk = sd(ave_sk, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Formatting the table with kable and kableExtra
sk_summary %>%
  kable("html") %>%
  kable_styling("striped", full_width = FALSE) %>%
  add_header_above(c(" " = 2, "Subjective Knowledge" = 3)) %>% # Corrected the number of columns
  column_spec(3:5, bold = TRUE, color = "blue") # Adjusted the column range



# Create the plot
ggplot(sk_summary, aes(x=sk_time, y=mean_ave_sk, group=text_type, color=text_type)) +
  geom_line(linewidth=1) + # Lines connecting the points
  geom_point(linewidth=3) + # Points for the means
  geom_errorbar(aes(ymin=mean_ave_sk - se_ave_sk, ymax=mean_ave_sk + se_ave_sk), width=0.2) + # Error bars
  labs(
    title="Effect of SK Time and Text Type on Average SK",
    x="SK Time",
    y="Average SK"
  ) +
  ylim(1, 7) + # Set the limits of the Y-axis
  theme_minimal() +
  scale_color_brewer(palette="Set1") # Use a color palette for the different text types
```

# Objective Knowledge

```{r OK data frames and summary}

ok_df <- exp_data_t %>%
  select(ResponseId, total_ok, text_type, wta_moment, pilot)

ok_df <- na.omit(ok_df) # Remove missing values

ok_summary <- ok_df %>%
  group_by(text_type, wta_moment) %>%
  summarise(
    n_obs = n(),
    mean_total_ok = mean(total_ok, na.rm = TRUE),
    se_total_ok = sd(total_ok, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

ok_summary %>%
  kable("html") %>%
  kable_styling("striped", full_width = F) %>%
  add_header_above(c("Summary Statistics" = 5), font_size = 15) %>%
  column_spec(1, bold = T, color = "blue") %>%
  column_spec(2, italic = T)

```

## Two-way Anova for OK

```{r}
# Run the two-way ANOVA
anova_ok <- aov(total_ok ~ text_type * wta_moment, data = ok_df)

#anova_ok <- aov(total_ok ~ text_type * pilot, data = ok_df)

#summary(anova_ok2)

# Print the summary of the ANOVA
summary(anova_ok)

# Compute the means and standard errors for each combination of text_type and wta_moment
ok_summary <- ok_df %>%
  group_by(text_type, wta_moment) %>%
  summarise(
    n_obs = n(),
    mean_total_ok = mean(total_ok, na.rm = TRUE),
    se_total_ok = sd(total_ok, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Now we can create a ggplot with both independent variables
ggplot(ok_summary, aes(x = text_type, y = mean_total_ok, group = wta_moment, color = wta_moment)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_total_ok - se_total_ok, ymax = mean_total_ok + se_total_ok), width = 0.2) +
  labs(title = "Interaction between Text Type and WTA Moment",
       x = "Text Type",
       y = "Mean Total OK",
       color = "WTA Moment") +
  ylim(1,9) +
  theme_minimal()
```


# WTA

```{r wta summary}
wta_df <- exp_data_t %>%
  select(ResponseId, total_ok, text_type, wta_moment, ave_wta, ave_sk_t1, ave_sk_t2, ave_sk_t3)

wta_df <- na.omit(wta_df)

wta_summary <- wta_df %>%
  group_by(text_type, wta_moment) %>%
  summarise(
    n_obs = n(), # Number of observations per group
    mean_wta_ok = mean(ave_wta, na.rm = TRUE),
    se_wta_ok = sd(ave_wta, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

wta_summary %>%
  kable("html") %>%
  kable_styling("striped", full_width = F) %>%
  add_header_above(c("Summary Statistics" = 5), font_size = 15) %>%
  column_spec(1, bold = T, color = "blue") %>%
  column_spec(2, italic = T)

```

```{r wta ANOVA}
# Run the two-way ANOVA
anova_wta <- aov(ave_wta ~ text_type * wta_moment, data = wta_df)

# Print the summary of the ANOVA
summary(anova_wta)


library(ggplot2)
library(dplyr)


# Create the line plot with y-axis limits set from 0 to 10, and add standard error bars
ggplot(wta_summary, aes(x = text_type, y = mean_wta_ok, color = wta_moment, group = wta_moment)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_wta_ok - se_wta_ok, ymax = mean_wta_ok + se_wta_ok), width = 0.2) +
  labs(title = "Interaction Plot",
       subtitle = "Effects of text_type and wta_moment on ave_wpa",
       x = "Text Type",
       y = "Mean of WTA",
       color = "WTA Moment") +
  ylim(0, 5) +  # Set y-axis limits
  theme_minimal()
```

